DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-06-15 paper/evaluation-drampart.tex
Minor changes

In this subsection, we examine the CNN workload's memory bandwidth
sensitivity and the effect of memory bandwidth throttling in providing
isolation. For the experiments, we use MemGuard\cite{Yun2013}, a Linux
kernel module that can limit the amount of memory bandwidth each core
receives. MemGuard
operates periodically, at a 1 ms interval, and uses hardware
performance counters to throttle cores, if they exceed their given
bandwidth budgets within each regulation period (i.e., 1 ms), by
scheduling high-priority idle kernel threads until the next period begins.

>>>>

In this subsection, we examine the CNN workload's memory bandwidth
sensitivity and the effect of memory bandwidth throttling in providing
isolation. For the experiments, we use MemGuard\cite{Yun2013}, a Linux
kernel module that can limit the amount of memory bandwidth each core
receives. MemGuard
operates periodically, at a 1 ms interval, and uses hardware
performance counters to throttle cores if they exceed their given
bandwidth budgets within each regulation period (i.e., 1 ms), by
scheduling high-priority idle kernel threads until the next period begins.

### 2018-06-15 paper/evaluation.tex
Minor changes

Figure~\ref{fig:perf_vs_bandwidth} shows the results. Note
that BwWrite co-runners cause significantly higher execution time
increases---up to 11.6X---on CNN inferencing while BwRead co-runners
cause relatively much smaller time increases. While execution time
increases are expected, the degree to which that is seen in the worst-case 
is quite surprising---\emph{if the CNN controller was driving an actual 
car, it would result in a car crash!}

>>>>

Figure~\ref{fig:perf_vs_bandwidth} shows the results. Note
that BwWrite co-runners cause significantly higher execution time
increases---up to 11.6X---on CNN inferencing while BwRead co-runners
cause relatively much smaller time increases. While execution time
increases are expected, the degree to which it is seen in the worst-case 
is quite surprising---\emph{if the CNN controller was driving an actual
car, it would result in a car crash!}

### 2018-06-15 paper/related.tex
Minor changes

In this paper, we have analyzed real-time performance of a real-world
CNN, which was used in NVIDIA's DAVE-2 self-driving
car~\cite{Bojarski2016}, on a low-cost raspberry pi 3 quad-core 
platform and other embedded multicore platforms. It should be noted, 
however, that DAVE-2's CNN is relatively small compared
to recent state-of-the-art CNNs, which are increasingly larger and
deeper. For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters, which are much larger than DAVE-2's CNN.
Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.

>>>>

In this paper, we have analyzed real-time performance of a real-world
CNN, which was used in NVIDIA's DAVE-2 self-driving
car~\cite{Bojarski2016}, on a low-cost Raspberry Pi 3 quad-core 
platform and other embedded multicore platforms. It should be noted,
however, that DAVE-2's CNN is relatively small compared
to recent state-of-the-art CNNs, which are increasingly larger and
deeper. For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters, which are much larger than DAVE-2's CNN.
Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.
